[Artifact57] Robust Resource Bounds with\\ Static Analysis and Bayesian Inference

### 2024-03-11 README/getting_started_guide.tex
Updated the explanation of hyperparameters

Our artifact, dubbed Hybrid Resource-Aware ML (Hybrid RaML), is a program analysis tool
that takes in an OCaml program and infers its worst-case polynomial cost bound
using the technique Hybrid AARA described in the paper.
%
Hybrid AARA integrates data-driven resource analysis (i.e., inferring a cost
bound from the runtime cost measurements of the program) and static resource
analysis (i.e., inferring a cost bound from the source code of the program).

@@

The configuration file \texttt{config\_bayeswc.json} for \BayesWC{} specifies
(i) the probabilistic model hyperparameters $\beta$ and $s$ in Weibull survival
analysis\footnote{Explained in this PyMC tutorial:
  \url{https://www.pymc.io/projects/examples/en/2022.12.0/survival_analysis/bayes_param_survival_pymc3.html}}
and (ii) the inference hyperparameters such as the number of chains and the
number of iterations to run in a sampling-based Bayesian inference algorithm.

The configuration file \texttt{config\_bayespc.json} for \BayesPC{} contains (i)
the probabilistic model hyperparameters for Gaussian and Weibull distributions
and (ii) the inference hyperparameters for reflective Hamiltonian Monte Carlo
(HMC) used in \BayesWC{}.
%
Reflective HMC runs a sampling-based Bayesian inference algorithm within a
feasible region of a linear program.

>>>>

Our artifact, dubbed Hybrid Resource-Aware ML (Hybrid RaML), is a program analysis tool
that takes in an OCaml program and infers its worst-case polynomial cost bound
using the technique Hybrid AARA developed in the paper.
%
Hybrid AARA integrates data-driven resource analysis (i.e., inferring a cost
bound from the runtime cost measurements of the program) and static resource
analysis (i.e., inferring a cost bound from the source code of the program).

@@

The configuration file \texttt{config\_bayeswc.json} for \BayesWC{} specifies
(i) the probabilistic model hyperparameter $\gamma_0$ in Weibull survival
analysis\footnote{See Appendix~C of the updated version of the paper. The
probabilistic model is also explained in this PyMC tutorial:
\url{https://www.pymc.io/projects/examples/en/2022.12.0/survival_analysis/bayes_param_survival_pymc3.html}.}
and (ii) the inference hyperparameters such as the number of chains and the
number of iterations to run in a sampling-based Bayesian inference algorithm.

The configuration file \texttt{config\_bayespc.json} for \BayesPC{} contains (i)
the probabilistic model hyperparameters $\gamma_0$ for normal prior
distributions and $\theta_0, \theta_1$ for Weibull prior distributions and (ii)
the inference hyperparameters for reflective Hamiltonian Monte Carlo (HMC) used
in \BayesPC{}.
%
Reflective HMC runs a sampling-based Bayesian inference algorithm within a
feasible region of a linear program.
